Late Fusion via Subspace Search with Consistency Preservation

### 2017-03-12 egpaper_for_review.tex
small change

To prevent from the expensive nuclear norm minimization,
in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low-rank label matrix.
Particularly, our method searches the solution in a low-rank subspace under a fixed-rank constraint.
As for outlier detection,
we propose to filter out these inconsistent predictions on specific classes of models (See Fig.\ref{fig:framework}.
Notations are introduced shortly.).
The $\ell_{1,2}$ loss preserves the fidelity within each column by $L_2$ loss in the vertical direction and is robust to sparse errors across all the columns by $L_1$ loss in the horizontal direction.
However, the single $L_2$ doesn't have the ability to detect outliers and the single $L_1$ has the instability property.
Based on this observation, we apply this robust $\ell_{1,2}$ loss to remove the outlier columns in the label indicator matrix.
Furthermore, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the non-smooth loss.
We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to non-smooth problems.

@@

%Our proposed late fusion algorithm is based on matrix factorization,
%which has attracted increasing attention recently.
Matrix factorization has attracted increasing attention recently.
Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry in a subspace.
Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank}.
In~\cite{vandereycken2013lowrank}, the authors propose a low-rank geometric conjugate gradient (LRGeomCG) method.
In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low-rank matrix completion by exploiting the low-rank constraint.
In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
However, all these matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.
Moreover, \cite{jain2013low} can also be used for matrix completion based on alternating minimization,
but they require the incoherent matrix assumption and a fresh measurements at each iteration.
Thus their method can not be guaranteed to converge the global solution in our work.
In addition, as shown in \cite{vandereycken2013lowrank}, the Riemannian manifold method converges faster than the alternating minimization approach.

@@

The previous ALM methods~\cite{liu2013robust} usually focus on the convex problem,
but Problem~(\ref{eq:l12_mf}) is the non-convex problem.
We proof the convergence of ALM for solving a non-convex problem relying on the gradient, as following:

\begin{theorem}
\label{theorem:alm_convergence}
  Suppose the sequences $\{\bX_k\}_{k=1}^{\infty}$, $\{\bE_k\}_{k=1}^{\infty}$ and $\{\blambda_k\}_{k=1}^{\infty}$ are generated by Algorithm~\ref{alg:alm_mf},
  and $\{\blambda_k\}$ is bounded.
  As $k \to \infty$, the gradient of $\calL$ vanishes,
  thus any accumulation point $(\bX^*, \bE^*)$ is a stationary point.
\end{theorem}

@@

@@

%% Flower 17 Time [3.14] [229] [0.26] [1.62]

@@

\begin{table*}[t]
\centering
\begin{tabular}{c|c|c|c|c|c}
\hline
Method              & UCF-101          & CIFAR-10         & CIFAR-100        & Oxford-IIIT-Pet & PASCAL VOC 2007    \\\hline
ASF                 & 86.78\%          & 94.21\%          & 76.91\%          & 92.46\%         &   90.51\%          \\
MKL                 & 85.38\%          & 94.15\%          & 72.71\%          & 87.13\%         &   85.82\%          \\
RCEC                & 86.60\%          & 94.99\%          & 77.13\%          & 92.11\%         &   90.92\%          \\
FWOT                & -                & -                & -                & 92.90\%         &   91.20\%          \\
LPBoost             & 86.24\%          & 94.88\%          & 76.59\%          & 92.73\%         &   91.42\%          \\\hline
\textbf{Ours}       & \textbf{89.03\%} & \textbf{95.11\%} & \textbf{77.72\%} & \textbf{92.90\%}&   90.98\%          \\
\hline
\end{tabular}
\caption{Mean accuracy on real-world data sets.
FWOT costs excessive time for training UCF-101, CIFAR-10 , CIFAR-100~(over 24 hours),
so we omit these results indicated by ``-''.
}
\label{table:total_acc}
\end{table*}

\begin{table*}[t]
\centering
\begin{tabular}{c|c|c|c|c|c}
\hline
Method              & UCF-101    & CIFAR-10  & CIFAR-100  & Oxford-IIIT-Pet & PASCAL VOC 2007 \\\hline
RCEC                & 86.60      & 81.41     &  255.51    & 18.82           &   16.45         \\
FWOT                & $\infty$   & $\infty$  &  $\infty$  & 61697           &   19674         \\
LPBoost             & 110.81     & 72.45     &  4750.9    & 43.67           &   7.46          \\\hline
Ours                & 421.23     & 5.384     &  417.26    & 76.16           &   16.21         \\
\hline
\end{tabular}
\caption{Experimental results on real-world data sets. Computational time is recorded in seconds.
FWOT costs excessive time for training UCF-101, CIFAR-10 , CIFAR-100~(over 24 hours),
so we omit these results indicated by ``$\infty$''.}
\label{table:total_time}
\end{table*}

@@

For action recognition, we present the comparison results on UCF 101 dataset.
UCF101 contains 13320 videos collected from YouTube, categorized into 101 human action classes.
We use the official split-1 described in~\cite{soomro2012ucf101}, which have 9573 training videos and 3783 testing videos.
As mentioned above, we extract fives features and train different classifier on each feature with the default parameters by LIBLINEAR.
Then by applying five classifiers on test data, we obtain $5 \times 101$ confidence scores for each video, which forms the input matrix $\bX$ of our algorithm.
Results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}, in which we illustrate the performance of six fusion methods.
To be noted, FWOT is too slow to train, we do not show its result (more than one day).

%\subsubsection{Experiment on Cifar10 dataset}

@@

As we have 50000 training data and 10000 testing data,
FWOT algorithm has one step to deal with $n\times n$ matrixes, which are excessive to train~(more than one day).
LPBoost algorithm needs to create a $(n\calC - n) \times (1 + n + m)$ constraint matrix linear programming solvers
\footnote{\cite{gehler2009feature} use the MOSEK interior-point solver, see www.mosek.com.},
which occupies too much memory and still consumes long time to train,
so we solve this problem by using sparse matrices and parallel computation in MATLAB.
We also use `-s 2' parameters in LIBLINEAR to speedup training process.
Results of total six compared algorithms are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.

CIFAR-100 is similar with CIFAR-10, except it has 100 classes containing 600 images each.
There are 50000 training data and 10000 testing data as CIFAR-10.
Twelve CNN features used in this experiment are described in the feature selection section.
Training and comparison process are the same as CIFAR-10.
Detailed results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.

The Oxford-IIIT-Pet dataset contains 7349 images covering 37 different breeds of cats and dogs, 2371 images for cats and 4978 images for dogs.
There are roughly 200 pictures in each category with a large variations in multiple views, such as pose, scale and lighting.
We randomly sample fifty percent pictures as our training data and the others as testing data.
And then we train svm on each single feature and fuse the predictions by our proposed method.
We repeat the sample , training and fusion process five times to get fair results.
The comparison results are shown in Table~\ref{table:total_acc} and \ref{table:total_time}.

@@

From Table~\ref{table:total_acc}, our proposed algorithm provides significant improvement comparing with other effective late fusion methods on most datasets.
Additionally, our algorithm is more efficient than other late fusion methods in most situations.
As we can see from Table~\ref{table:total_time}, some methods are not capable of handling large scale dataset.
However, ours can solve the large scale problem efficiently.
%For example, the cost of FWOT is tremendous
%and it takes more than one day to fuse multiple results on CIFAR and UCF-101.
%With the growth of class number, LPBoost costs too much on data preparation affecting the overall efficiency.
%RCEC is usually faster than ours, but ours classification performance is better than its.

@@

\begin{table}[ht]
\centering
\begin{tabular}{c|c|c|c}
\hline
Strategy            & Wikipedia         & Flowers 17          & Pascal Sentence     \\\hline
[AVE]               & 47.78\%           & \textbf{96.77\%}    & 66.40\%             \\\hline
[VOTE]              & 47.85\%           & 96.61\%             & 66.20\%             \\\hline
[GATE]              & \textbf{49.03\%}  & \textbf{96.77\%}    & \textbf{67.20\%}    \\
\hline
\end{tabular}
\caption{Mean accuracy using different strategies on three datasets.}
\label{table:strategy}
\end{table}

@@

In this sub-section, we compare the performance of our algorithm with the state-of-the-art techniques.
%we demonstrate experiments to compare the performance of our algorithm with the state-of-the-art techniques.
We use SVM classifiers based on different features in previous experiments to make a fair comparison with some MKL based methods.
Since the performance of SVM classifiers usually are not as good as the results directly predicted by CNN models,
in order to obtain a higher result, we directly fuse multiple state-of-the-art CNN predictions.
Then we demonstrate the improvement of our fusion results compared to the state-of-the-art single model performance in Table.\ref{table:state_of_the_art}.

\begin{table}[ht]
\begin{center}
\begin{tabular}{ c | c | c }
    \hline
                                              & CIFAR-10             & CIFAR-100  \\\hline
\multirow{2}{*}{ResNet~\cite{he2016identity}} & 110, 134, 164        & 56, 110, 164  \\
                                              & $164^{*}$, $200^{*}$ & $110^{*}$, $164^{*}$  \\\hline
\multirow{2}{*}{WRN~\cite{zagoruyko2016wide}} & 16-10, 22-8, 28-10   & 16-10, 22-8, 28-10  \\
                                              &    40-4, 40-8        & 40-4  \\\hline
NIN~\cite{lin2013network}                     &     -                & -  \\ \hline
\end{tabular}
\end{center}
\caption{Model selection for CIFAR-10 dataset.
In the ResNet block, numbers represent the depth of the selected models.
``*'' represents using the bottleneck block, otherwise using the basic block in residual networks.
In WRN block, ``x-y'', x represents the depth, and y represents the widening factor.
NIN network has only one formula, so we do not list its depth.}
\label{table:models}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{c|c|c}\hline
                                                    &  CIFAR-10 & CIFAR-100  \\\hline
NIN~\cite{lin2013network}                           &   8.81    &  35.67     \\\hline
Highway~\cite{srivastava2015highway}                &   7.72    &  32.39     \\\hline
ELU~\cite{clevert2015fast}                          &   6.55    &  24.28     \\\hline
Pre-ResNet-1001~\cite{he2016identity}               &   4.92    &  22.71     \\\hline
WRN-28-10~\cite{zagoruyko2016wide}                  &   4.17    &  20.50     \\\hline
ResNeXt-29, $16\times64d$~\cite{xie2016aggregated}  &   3.58    &  17.31     \\\hline
Ours                                                &   3.47    &  17.24     \\\hline
\end{tabular}
\caption{Test error of different methods on CIFAR-10 and CIFAR-100 for different architectures.
}
\label{table:state_of_the_art}
\end{table}

We carefully cite the best performances reported in their papers
\cite{clevert2015fast,he2016identity,lin2013network,srivastava2015highway,xie2016aggregated,zagoruyko2016wide}
As we can observe, our fusion is capable of further improving the performance of single model by a large margin.
A single model has limited performance even with deeper depth or wider channel.
However, our fusion algorithm can achieve further improvement when the single model reaches the limit.
To be noticed, our method fuses multiple single models which all perform worse than ResNeXt~\cite{xie2016aggregated},
but can achieve low test error.
This demonstrates the benefit of a good late fusion method.

>>>>

To prevent from the expensive nuclear norm minimization,
in this paper, we propose a more efficient matrix factorization algorithm to recover the underlying low-rank label matrix.
Particularly, our method searches the solution in a low-rank subspace under a fixed-rank constraint.
As for outlier detection,
we propose to filter out these inconsistent predictions on specific classes of models (See Fig.\ref{fig:framework}.
Notations are introduced shortly.).
\yanred{
The $\ell_{1,2}$ loss preserves the fidelity within each column by $L_2$ loss in the vertical direction and is robust to sparse errors across all the columns by $L_1$ loss in the horizontal direction.
However, the single $L_2$ doesn't have the ability to detect outliers and the single $L_1$ has the instability property.
Based on this observation, we apply this robust $\ell_{1,2}$ loss to remove the outlier columns in the label indicator matrix.
}
Furthermore, most existing matrix factorization optimization methods only consider smooth loss functions, rather than the non-smooth loss.
We thus in particular present an approach based on augmented Lagrangian multiplier (ALM) to extend matrix factorization methods to non-smooth problems.

@@

%Our proposed late fusion algorithm is based on matrix factorization,
%which has attracted increasing attention recently.
Matrix factorization has attracted increasing attention recently.
Many manifold optimization algorithms on matrix factorization have been proposed by exploiting the manifold geometry in a subspace.
Based on manifold optimization, fixed-rank matrices are supposed to belong to a smooth matrix manifold~\cite{Absil2008OAMM,vandereycken2013lowrank}.
In~\cite{vandereycken2013lowrank}, the authors propose a low-rank geometric conjugate gradient (LRGeomCG) method.
In~\cite{rtrmc2011boumal}, first- and second-order Riemannian trust-region methods are applied to solve the low-rank matrix completion by exploiting the low-rank constraint.
In~\cite{Bonnabel2011}, a linear regression algorithm is proposed, where the parameter of this algorithm is a fixed-rank matrix based on the Riemannian manifold geometry.
In~\cite{Mishra2012}, the authors propose a quotient geometric matrix completion method.
The authors in~\cite{grouse2010Balzano} propose an online algorithm for tracking subspaces, Grassmannian rank-one update subspace estimation.
In~\cite{ngonips2012scaled}, a gradient methods based on scaled metric on the Grassmann manifold is proposed.
The authors in~\cite{Wen2012} propose a low-rank matrix fitting algorithm to solve large scale matrix completion problems by exploiting nonlinear successive over-relaxation.
In~\cite{RechtNIPS2011hogwild}, a lock-free approach to parallelizing stochastic gradient descent is proposed.
However, all these matrix factorization methods only consider the general least square loss, which cannot be directly applied to handle $\ell_{1,2}$ loss.
\yanred{
Moreover, \cite{jain2013low} can also be used for matrix completion based on alternating minimization,
but they require the incoherent matrix assumption and a fresh measurements at each iteration.
Thus their method can not be guaranteed to converge the global solution in our work.
In addition, as shown in \cite{vandereycken2013lowrank}, the Riemannian manifold method converges faster than the alternating minimization approach.
}

@@

\yanred{
The previous ALM methods~\cite{liu2013robust} usually focus on the convex problem,
but Problem~(\ref{eq:l12_mf}) is the non-convex problem.
In addition, we proof the convergence of ALM for solving a non-convex problem relying on the gradient,
rather than the (xxxxxxxx) for convex problem,
as following:
}

\yanred{
\begin{theorem}
\label{theorem:alm_convergence}
  Suppose the sequences $\{\bX_k\}_{k=1}^{\infty}$, $\{\bE_k\}_{k=1}^{\infty}$ and $\{\blambda_k\}_{k=1}^{\infty}$ are generated by Algorithm~\ref{alg:alm_mf},
  and $\{\blambda_k\}$ is bounded.
  As $k \to \infty$, the gradient of $\calL$ vanishes,
  thus any accumulation point $(\bX^*, \bE^*)$ is a stationary point.
\end{theorem}
}

@@

\yanred{
\textbf{Reproducibility.}
Our implementation is modified from the open-sourced LRGeomCG
\cite{vandereycken2013lowrank}\footnote{http://www.unige.ch/math/vandereycken/matrix\_completion.html}.
We will release the source code soon.
}

@@

@@

\begin{table*}[t]
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Method              & UCF-101          & CIFAR-10         & CIFAR-100        & Oxford-IIIT-Pet  & PASCAL VOC 2007    \\\hline
ASF                 & 86.78\%          & 94.21\%          & 76.91\%          & 92.46\%          &   90.51\%          \\
MKL                 & 85.38\%          & 94.15\%          & 72.71\%          & 87.13\%          &   85.82\%          \\
RCEC                & 86.60\%          & 94.99\%          & 77.13\%          & 92.11\%          &   90.92\%          \\
FWOT                & -                & -                & -                & \textbf{92.90\%} &   91.20\%          \\
LPBoost             & 86.24\%          & 94.88\%          & 76.59\%          & 92.73\%          &   \textbf{91.42\%} \\\hline
\textbf{Ours}       & \textbf{89.03\%} & \textbf{95.11\%} & \textbf{77.72\%} & \textbf{92.90\%} &   90.98\%          \\
\hline
\end{tabular}
\caption{Mean accuracy on real-world data sets.
FWOT costs excessive time for training UCF-101, CIFAR-10 , CIFAR-100~(over 24 hours),
so we omit these results indicated by ``-''.
}
\label{table:total_acc}
\end{table*}

\begin{table*}[t]
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
Method              & UCF-101         & CIFAR-10        & CIFAR-100        & Oxford-IIIT-Pet & PASCAL VOC 2007 \\\hline
RCEC                & \textbf{86.60}  & 81.41           &  \textbf{255.51} & \textbf{18.82}  &   16.45         \\
FWOT                & $\infty$        & $\infty$        &  $\infty$        & 61697           &   19674         \\
LPBoost             & 110.81          & 72.45           &  4750.9          & 43.67           &   \textbf{7.46} \\\hline
Ours                & 421.23          & \textbf{5.384}  &  417.26          & 76.16           &   16.21         \\
\hline
\end{tabular}
\caption{Experimental results on real-world data sets. Computational time is recorded in seconds.
FWOT costs excessive time for training UCF-101, CIFAR-10 , CIFAR-100~(over 24 hours),
so we omit these results indicated by ``$\infty$''.}
\label{table:total_time}
\end{table*}

@@

For action recognition, we present the comparison results on UCF 101 dataset.
UCF101 contains 13320 videos collected from YouTube, categorized into 101 human action classes.
We use the official split-1 described in~\cite{soomro2012ucf101}, which have 9573 training videos and 3783 testing videos.
As mentioned above, we extract fives features and train different classifier on each feature with the default parameters by LIBLINEAR.
Then by applying five classifiers on test data, we obtain $5 \times 101$ confidence scores for each video, which forms the input matrix $\bX$ of our algorithm.
Results are shown in Table~\ref{table:total_acc} and Table~\ref{table:total_time}, in which we illustrate the performance of six fusion methods.
To be noted, FWOT is too slow to train, we do not show its result (more than one day).

@@

As we have 50000 training data and 10000 testing data,
FWOT algorithm has one step to deal with $n\times n$ matrixes, which are excessive to train~(more than one day).
LPBoost algorithm needs to create a $(n\calC - n) \times (1 + n + m)$ constraint matrix linear programming solvers
\footnote{\cite{gehler2009feature} use the MOSEK interior-point solver, see www.mosek.com.},
which occupies too much memory and still consumes long time to train,
so we solve this problem by using sparse matrices and parallel computation in MATLAB.
We also use `-s 2' parameters in LIBLINEAR to speedup training process.
Results of total six compared algorithms are shown in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.

CIFAR-100 is similar with CIFAR-10, except it has 100 classes containing 600 images each.
There are 50000 training data and 10000 testing data as CIFAR-10.
Twelve CNN features used in this experiment are described in the feature selection section.
Training and comparison process are the same as CIFAR-10.
Detailed results are shown in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.

The Oxford-IIIT-Pet dataset contains 7349 images covering 37 different breeds of cats and dogs, 2371 images for cats and 4978 images for dogs.
There are roughly 200 pictures in each category with a large variations in multiple views, such as pose, scale and lighting.
We randomly sample fifty percent pictures as our training data and the others as testing data.
And then we train svm on each single feature and fuse the predictions by our proposed method.
We repeat the sample , training and fusion process five times to get fair results.
The comparison results are shown in Table~\ref{table:total_acc} and Table~\ref{table:total_time}.

@@

From Table~\ref{table:total_acc}, our proposed algorithm provides significant improvement comparing with other effective late fusion methods on most datasets.
Additionally, our algorithm is more efficient than other late fusion methods in most situations.
As we can see from Table~\ref{table:total_time}, some methods are not capable of handling large scale dataset.
\yanred{
However, the time consumption of ours is acceptable in all experiments and quite fast on CIFAR-10/VOC2007.
In conclusion, our method can solve the large scale problem efficiently.
}

@@

\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|c|}
\hline
Strategy            & Wikipedia         & Flowers 17          & Pascal Sentence     \\\hline
[AVE]               & 47.78\%           & \textbf{96.77\%}    & 66.40\%             \\\hline
[VOTE]              & 47.85\%           & 96.61\%             & 66.20\%             \\\hline
[GATE]              & \textbf{49.03\%}  & \textbf{96.77\%}    & \textbf{67.20\%}    \\
\hline
\end{tabular}
\caption{Mean accuracy using different strategies on three datasets.}
\label{table:strategy}
\end{table}

@@

In this sub-section, we compare the performance of our algorithm with the state-of-the-art techniques.
%we demonstrate experiments to compare the performance of our algorithm with the state-of-the-art techniques.
We use SVM classifiers based on different features in previous experiments to make a fair comparison with some MKL based methods.
Since the performance of SVM classifiers usually are not as good as the results directly predicted by CNN models,
in order to obtain a higher result, we directly fuse multiple state-of-the-art CNN predictions.
Then we demonstrate the improvement of our fusion results compared to the state-of-the-art single model performance in Table~\ref{table:state_of_the_art}.

\begin{table}[ht]
\begin{center}
\begin{tabular}{| c | c | c |}
    \hline
                                              & CIFAR-10             & CIFAR-100  \\\hline
\multirow{2}{*}{ResNet~\cite{he2016identity}} & 110, 134, 164        & 56, 110, 164  \\
                                              & $164^{*}$, $200^{*}$ & $110^{*}$, $164^{*}$  \\\hline
\multirow{2}{*}{WRN~\cite{zagoruyko2016wide}} & 16-10, 22-8, 28-10   & 16-10, 22-8, 28-10  \\
                                              &    40-4, 40-8        & 40-4  \\\hline
NIN~\cite{lin2013network}                     &     -                & -  \\ \hline
\end{tabular}
\end{center}
\caption{Model selection for CIFAR-10 dataset.
In the ResNet block, numbers represent the depth of the selected models.
``*'' represents using the bottleneck block, otherwise using the basic block in residual networks.
In WRN block, ``x-y'', x represents the depth, and y represents the widening factor.
NIN network has only one formula, so we do not list its depth.}
\label{table:models}
\end{table}

\begin{table}[ht]
\centering
\begin{tabular}{|c|c|c|}\hline
    Methods                                         &  CIFAR-10       & CIFAR-100           \\\hline
NIN~\cite{lin2013network}                           &   8.81          &  35.67              \\\hline
Highway~\cite{srivastava2015highway}                &   7.72          &  32.39              \\\hline
ELU~\cite{clevert2015fast}                          &   6.55          &  24.28              \\\hline
Pre-ResNet-1001~\cite{he2016identity}               &   4.92          &  22.71              \\\hline
WRN-28-10~\cite{zagoruyko2016wide}                  &   4.17          &  20.50              \\\hline
ResNeXt-29, $16\times64d$~\cite{xie2016aggregated}  &   3.58          &  17.31              \\\hline
Ours                                                &   \textbf{3.47} &  \textbf{17.24}     \\\hline
\end{tabular}
\caption{Test error of different methods on CIFAR-10 and CIFAR-100 for different architectures.
}
\label{table:state_of_the_art}
\end{table}

We carefully cite the best performances reported in their papers
\cite{clevert2015fast,he2016identity,lin2013network,srivastava2015highway,xie2016aggregated,zagoruyko2016wide}.
\yanred{
As we can observe, our fusion is capable of further improving the performance of single model by a large margin.
A single model has limited performance even with deeper depth or wider channel.
However, our fusion algorithm can achieve further improvement when the single model reaches the limit.
To be noticed, our method fuses multiple single models which all perform worse than ResNeXt~\cite{xie2016aggregated},
but can achieve low test error.
This demonstrates the benefit of a good late fusion method.
}
